---
title: "Test slides"
author: "TX"
date: '2022-05-26'
output:
  ioslides_presentation:
    widescreen: yes
    logo: logo.png
---

<script>

    .gdbar img {
        width: 300px !important;
        height: 150px !important;
        margin: 8px 8px;
    }

    .gdbar {
        width: 400px !important;
        height: 170px !important;
    }

    slides > slide:not(.nobackground):before {
        width: 150px;
        height: 75px;
        background-size: 150px 75px;
    }

</script>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown {data-background=slide1.png data-background-size=cover}

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets {data-background=outline.png data-background-size=cover}

- Bullet 1
- Bullet 2
- Bullet 3

## Center the content {data-background=slide1.png data-background-size=cover}

```{r cars, echo = TRUE}
summary(cars)
```

## Test slides {data-background=slide1.png data-background-size=cover}

<div class="red2">
- Bullet 1
- Bullet 2
- Bullet 3
</div>

<div class="blue3">
- Bullet 1
- Bullet 2
- Bullet 3
</div>

## Slide with Plot {data-background=slide1.png data-background-size=cover}

```{r pressure, echo = TRUE}
### <b>
x <- 10
y <- x * 2
### </b>
plot(pressure)
```

## Student-t distribution {data-background=slide1.png data-background-size=cover}

```{r student-t, echo=TRUE}
x <- seq(-5, 5, by = 0.01)
y <- dt(x, df = Inf)
y2 <- dt(x, df = 10)
y3 <- dt(x, df = 5)
y4 <- dt(x, df = 3)
y5 <- dt(x, df = 1)
plot(y, type = "l", main = "t-distribution",col = "Red")
lines(y2,col = "Orange",)
lines(y3,col = "Green")
lines(y4,col = "Blue")
lines(y5,col = "Purple")
legend(800, 0.4, legend=c("df = Inf", "df = 10", "df = 5","df = 3", "df = 1"),
       col=c("Red", "Orange", "Green", "Blue", "Purple"), lty=1)
```

## {data-background=endslide.png}



