---
title: "Test Slidy"
author: "Tao Xiang"
date: '2022-06-02'
output:
  slidy_presentation:
    duration: 45
    footer: Copyright (c) 2022, Clinchoice
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Text format

- Plain text
- End a line with two spaces to start a new paragraph.
- *italics* and _italics_
- **bold** and __bold__
- <span style="color:red">color</span>
- superscript^2^
- ~~strikethrough~~
- [link](www.rstudio.com)

- # Header 1
- ## Header 2
- ### Header 3
- #### Header 4
- ##### Header 5
- ###### Header 6

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Student-t distribution {data-background=slide1.png data-background-size=cover}

```{r student-t, echo=TRUE}
x <- seq(-5, 5, by = 0.01)
y <- dt(x, df = Inf)
y2 <- dt(x, df = 10)
y3 <- dt(x, df = 5)
y4 <- dt(x, df = 3)
y5 <- dt(x, df = 1)
plot(y, type = "l", main = "t-distribution",col = "Red")
lines(y2,col = "Orange",)
lines(y3,col = "Green")
lines(y4,col = "Blue")
lines(y5,col = "Purple")
legend(800, 0.4, legend=c("df = Inf", "df = 10", "df = 5","df = 3", "df = 1"),
       col=c("Red", "Orange", "Green", "Blue", "Purple"), lty=1)
```

